The Heavy Photon Search Test Detector

### 2014-06-20 author_list_hps_PAC39_compact_alphabetical_order.tex
Alphabetical author list. Consistent notion of HPS Test Run.
Comments from Raphael Dupre on draft v2.
Adding changes suggested by Larry Weinstein to 2nd draft.
New author list from EC.
Fixed order of Valery and Alex.
Fixed UCSC name in author list

\newcommand{\red[1]}{{\color{red}{\bf #1}}}
\newcommand{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand{\CUA}{Catholic University of America, Washington, D.C. 20064}
\newcommand{\OU}{Ohio University,  Athens, Ohio 45701}
\newcommand{\YEREVAN}{Yerevan Physics Institute, 375036 Yerevan, Armenia}
\newcommand{\SCAROLINA}{University of South Carolina, Columbia, South Carolina 29208}
\newcommand{\NSU}{Norfolk State University, Norfolk, Virginia 23504}
\newcommand{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
\newcommand{\genova}{Istituto Nazionale di Fisica Nucleare, Sezione di Genova e Dipartimento di Fisica dell\'Universita, 16146 Genova, Italy}
\newcommand{\SACLAY}{CEA, Centre de Saclay, Irfu/Service de Physique Nucl\'eaire 91191 Gif-sur-Yvette, France}
\newcommand{\ORSAY}{Institut de Physique Nucleaire d'Orsay, IN2P3, BP 1, 91406 Orsay, France}
\newcommand{\ECOLE}{CPhT, Ecole Polytechnique, F 91128 PALAISEAU CEDEX, France}
\newcommand{\UCSC}{University of California, Santa Cruz, CA 95064}
\newcommand{\SUNY}{Stony Brook University, Stony Brook, NY 11794-3800}
\newcommand{\FNAL}{Fermi National Accelerator Laboratory, Batavia, IL 60510-5011}
\newcommand{\UNH}{University of New Hampshire, Department of Physics, Durham, NH 03824}
\newcommand{\PERIMETER}{Perimeter Institute, Ontario, Canada N2L 2Y5}
\newcommand{\RPI}{Rensselaer Polytechnic Institute, Department of Physics, Troy, NY 12181}
\newcommand{\SLAC}{SLAC National Accelerator Laboratory, Menlo Park, CA 94025}
\newcommand{\WNM}{The College of William and Mary, Department of Physics, Williamsburg, VA 23185}

\author[SLAC]{C. Field}
\author[SLAC]{P. Hansson Adrian\corref{corrauthor}}
\author[SLAC]{N. Graf} 
\author[SLAC]{ M. Graham} 
\author[SLAC]{ G. Haller} 
\author[SLAC]{ R. Herbst} 
%\author[SLAC]{ J. Jaros\corref{spoks}} 
\author[SLAC]{ J. Jaros}
\author[SLAC]{T. Maruyama} 
\author[SLAC]{ J. McCormick} 
\author[SLAC]{ K. Moffeit} 
\author[SLAC]{ T. Nelson} 
\author[SLAC]{ H. Neal} 
\author[SLAC]{ A. Odian} 
\author[SLAC]{ M. Oriunno} 
\author[SLAC]{ S. Uemura} 
\author[SLAC]{ D. Walz}
%
\author[UCSC]{A. Grillo} 
\author[UCSC]{ V. Fadeyev} 
\author[UCSC]{ O. Moreno}
%
\author[FNAL]{W. Cooper}
%
\author[JLAB]{S. Boyarinov} 
\author[JLAB]{ V. Burkert} 
\author[JLAB]{ A. Deur} 
\author[JLAB]{ H. Egiyan}
 \author[JLAB]{ L. Elouadrhiri} 
 \author[JLAB]{ A. Freyberger} 
 \author[JLAB]{ F.-X. Girod} 
 \author[JLAB]{ V. Kubarovsky} 
\author[JLAB]{ Y. Sharabian} 
%\author[JLAB]{ S. Stepanyan\corref{spoks}} 
\author[JLAB]{ S. Stepanyan}
\author[JLAB]{ M. Ungaro} 
\author[JLAB]{ B. Wojtsekhowski}
%
\author[SUNY]{R. Essig}
%
%\author[UNH]{M. Holtrop\corref{spoks}} 
\author[UNH]{M. Holtrop}
\author[UNH]{ K. Slifer} 
\author[UNH]{ S. K. Phillips}
%
\author[ORSAY]{A. Fradi} 
\author[ORSAY]{ B. Guegan} 
\author[ORSAY]{ M. Guidal} 
\author[ORSAY]{ S. Niccolai} 
\author[ORSAY]{ S. Pisano} 
\author[ORSAY]{ E. Rauly}
\author[ORSAY]{ P. Rosier}
\author[ORSAY]{D. Sokhan}
 %
\author[PERIMETER]{P. Schuster} 
\author[PERIMETER]{ N. Toro}
%
\author[YEREVAN]{N. Dashyan} 
\author[YEREVAN]{ N. Gevorgyan} 
\author[YEREVAN]{ R. Paremuzyan}
\author[YEREVAN]{ H. Voskanyan}
%
\author[NSU]{M. Khandaker} 
\author[NSU]{ C. Salgado}
%
\author[GENOVA]{M. Battaglieri} 
\author[GENOVA]{ R. De Vita}
%
\author[ODU]{S. Bueltmann} 
\author[ODU]{ L. Weinstein}
%
\author[RPI]{P. Stoler} 
\author[RPI]{A. Kubarovsky}
%
\author[WNM]{K. Griffioen}

\address[SLAC]{\SLAC}                                 
\address[UCSC]{\UCSC}
\address[FNAL]{\FNAL}
\address[JLAB]{\JLAB}
\address[SUNY]{\SUNY}
\address[UNH]{\UNH}
\address[ORSAY]{\ORSAY}
\address[PERIMETER]{\PERIMETER}
\address[YEREVAN]{\YEREVAN}
\address[NSU]{\NSU}
\address[GENOVA]{\genova}
\address[ODU]{\ODU}
\address[RPI]{\RPI}
\address[WNM]{\WNM}

 %\cortext[spoks]{Co-spokesperson}

\cortext[corrauthor]{Corresponding author. \ead{phansson@slac.stanford.edu}}

>>>>

\newcommand{\red[1]}{{\color{red}{\bf #1}}}
\newcommand{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand{\CUA}{Catholic University of America, Washington, D.C. 20064}
\newcommand{\OU}{Ohio University,  Athens, Ohio 45701}
\newcommand{\YEREVAN}{Yerevan Physics Institute, 375036 Yerevan, Armenia}
\newcommand{\SCAROLINA}{University of South Carolina, Columbia, South Carolina 29208}
\newcommand{\NSU}{Norfolk State University, Norfolk, Virginia 23504}
\newcommand{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
\newcommand{\genova}{Istituto Nazionale di Fisica Nucleare, Sezione di Genova e Dipartimento di Fisica dell\'Universita, 16146 Genova, Italy}
\newcommand{\SACLAY}{CEA, Centre de Saclay, Irfu/Service de Physique Nucl\'eaire 91191 Gif-sur-Yvette, France}
\newcommand{\ORSAY}{Institut de Physique Nucleaire d'Orsay, IN2P3, BP 1, 91406 Orsay, France}
\newcommand{\ECOLE}{CPhT, Ecole Polytechnique, F 91128 PALAISEAU CEDEX, France}
\newcommand{\UCSC}{Santa Cruz Institute for Particle Physics, University of California, Santa Cruz, CA 95064}
\newcommand{\SUNY}{Stony Brook University, Stony Brook, NY 11794-3800}
\newcommand{\FNAL}{Fermi National Accelerator Laboratory, Batavia, IL 60510-5011}
\newcommand{\UNH}{University of New Hampshire, Department of Physics, Durham, NH 03824}
\newcommand{\PERIMETER}{Perimeter Institute, Ontario, Canada N2L 2Y5}
\newcommand{\RPI}{Rensselaer Polytechnic Institute, Department of Physics, Troy, NY 12181}
\newcommand{\SLAC}{SLAC National Accelerator Laboratory, Menlo Park, CA 94025}
\newcommand{\WNM}{The College of William and Mary, Department of Physics, Williamsburg, VA 23185}
\newcommand{\GLASGOW}{University of Glasgow, Glasgow, G12 8QQ, Scotland, UK}
\newcommand{\RUTGERS}{Rutgers University, Department of Physics and Astronomy, Piscataway, NJ 08854}

\author[GENOVA]{M. Battaglieri} 
\author[JLAB]{S. Boyarinov} 
\author[ODU]{S. Bueltmann} 
\author[JLAB]{ V. Burkert} 
\author[FNAL]{W. Cooper}
\author[JLAB]{C. Cuevas}
\author[YEREVAN]{N. Dashyan} 
\author[GENOVA]{ R. DeVita}
\author[ORSAY]{ C. Desnault}
\author[JLAB]{ A. Deur} 
\author[JLAB]{ H. Egiyan}
 \author[JLAB]{ L. Elouadrhiri} 
\author[SUNY]{R. Essig}
\author[UCSC]{ V. Fadeyev} 
\author[SLAC]{C. Field}
 \author[JLAB]{ A. Freyberger} 
\author[RUTGERS]{Y. Gershtein}
\author[YEREVAN]{ N. Gevorgyan} 
 \author[JLAB]{ F.-X. Girod} 
\author[SLAC]{N. Graf} 
\author[SLAC]{ M. Graham} 
\author[WNM]{K. Griffioen}
\author[UCSC]{A. Grillo} 
\author[ORSAY]{ M. Guidal} 
\author[SLAC]{ G. Haller} 
\author[SLAC]{P. Hansson Adrian\corref{corrauthor}}
\ead{phansson@slac.stanford.edu}
\author[SLAC]{ R. Herbst} 
\author[UNH]{M. Holtrop}
\author[SLAC]{ J. Jaros}
 \author[JLAB]{ S. Kaneta}
\author[NSU]{M. Khandaker} 
\author[RPI]{A. Kubarovsky}
\author[JLAB]{ V. Kubarovsky} 
\author[SLAC]{T. Maruyama} 
\author[SLAC]{ J. McCormick} 
\author[SLAC]{ K. Moffeit} 
\author[UCSC]{ O. Moreno}
\author[SLAC]{ H. Neal} 
\author[SLAC]{ T. Nelson} 
\author[ORSAY]{ S. Niccolai} 
\author[SLAC]{ A. Odian} 
\author[SLAC]{ M. Oriunno} 
\author[YEREVAN]{ R. Paremuzyan}
\author[SLAC]{ R. Partridge} 
\author[UNH]{ S. K. Phillips}
\author[ORSAY]{ E. Rauly}
 \author[JLAB]{ B. Raydo} 
\author[RUTGERS]{J. Reichert}
\author[ORSAY]{ E. Rindel} 
\author[ORSAY]{ P. Rosier}
\author[NSU]{ C. Salgado}
\author[PERIMETER]{P. Schuster} 
\author[JLAB]{ Y. Sharabian} 
\author[GLASGOW]{D. Sokhan}
\author[JLAB]{ S. Stepanyan}
\author[PERIMETER]{ N. Toro}
\author[SLAC]{ S. Uemura} 
\author[JLAB]{ M. Ungaro} 
\author[YEREVAN]{ H. Voskanyan}
\author[SLAC]{ D. Walz}
\author[ODU]{ L. B. Weinstein}
\author[JLAB]{ B. Wojtsekhowski}
%
%
%
%
%
%
 %
%
%
%
%
%
%
%
%

\address[GENOVA]{\genova}
\address[JLAB]{\JLAB}
\address[ODU]{\ODU}
\address[FNAL]{\FNAL}
\address[YEREVAN]{\YEREVAN}
\address[ORSAY]{\ORSAY}
\address[SUNY]{\SUNY}
\address[UCSC]{\UCSC}
\address[SLAC]{\SLAC}                                 
\address[RUTGERS]{\RUTGERS}
\address[WNM]{\WNM}
\address[UNH]{\UNH}
\address[NSU]{\NSU}
\address[RPI]{\RPI}
\address[PERIMETER]{\PERIMETER}
\address[GLASGOW]{\GLASGOW}

\cortext[corrauthor]{Corresponding author.}
